si: code and prose exploring Spatial Interaction models

### 2024-02-01 README.qmd

@@

>>>>

To get the develoment version do:

```{r}
devtools::load_all()
```

@@

```{r}
#| echo: false
#| eval: false
# Benmarks
bench::mark(
  {od_res = si_calculate(
  od,
  fun = gravity_model,
  d = distance_euclidean,
  m = origin_all,
  n = destination_all,
  constraint_production = origin_all,
  beta = 0.9
  )}
)
```

```{r}
#| echo: false
#| eval: false
# Add actions:
usethis::use_github_action("check-standard")
# Add pkgdown action:
usethis::use_github_action("pkgdown")
```
